\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape Ankit Kumar} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-9373078960 ~ \href{mailto:ankit.kumar19@iiitg.ac.in}{\raisebox{-0.2\height}\faEnvelope\  \underline{ankit.kumar19@iiitg.ac.in}} ~ 
    \href{https://linkedin.com/in/mynameisankit}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/mynameisankit}}  ~
    \href{https://github.com/mynameisankit}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/mynameisankit}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Guwahati}{Aug 2019 -- April 2023}
      {Bachelor of Technology in Computer Science and Engineering}{Guwahati, Assam}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Linear Algebra
                \item Algorithms Analysis
                \item Database Systems
                \item Artificial Intelligence
                \item Calculus
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
% \section{Experience}
%   \resumeSubHeadingListStart

%     \resumeSubheading
%       {Lorem Ipusm}{May 2020 -- August 2020}
%       {Software Engineer Intern}{City, State}
%       \resumeItemListStart
%         \resumeItem{Lorem Ipusm}
%       \resumeItemListEnd
    
%   \resumeSubHeadingListEnd
% \vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{Jeevan Sahyaak} $|$ \emph{Next.js, Material-UI, React.js, Express.js, React Native}}{May 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Conceptualised and developing a centralised system to help COVID patients to contact plasma donors as well as helping the volunteers find the needy near their localities.}
            \resumeItem{Developing a portal for relevant tweets on twitter, information and news regarding COVID and NGOs.}
            \resumeItem{\textbf{Proposed Work:} Develop a mobile app equivalent for the same using React Native.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Real Estate Management System} $|$ \emph{Next.js, MySQL, Material-UI, React.js, Express.js, Electron.js}}{April 2021}
          \resumeItemListStart
            \resumeItem{Designed and developed Entity-Relationship diagrams and SQL Tables}
            \resumeItem{Implemented an authentication system, separate interfaces for buyers, sellers and agents and a dashboard for admins with filtering feature to get only the data they  / need.}
            \resumeItem{Implemented a report generating feature to generate relevant charts and statistics based on successful deals a agent performs to enable admins to observe their performance.}
            \resumeItem{Created a XAMPP server on EC2 instance of AWS and hosted MySQL to remotely work with the database.}
            \resumeItem{\textbf{Proposed Work:} Develop an electron.js equivalent for the portal.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{IIITG Technical Board Portal} $|$ \emph{React.js, React Bootstrap, Material-UI, Firebase}}{February 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developed the SPA's for the technical board and clubs under it using React Bootstrap and various clubs under it and all of them uses client-side data fetching strategy using the firebase firestore and firebase API.}
            \resumeItem{Developed a Admin Dashboard using Material-UI to add / edit the content of the pages by directly interacting with the database.}
            \resumeItem{Implemented various input forms and a Drag-and-Drop feature to add new images.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: C, C++, JavaScript, Java, Python, BASH, HTML/CSS } \\
      \textbf{Databases}{: MySQL/MariaDB, PostgreSQL, Firebase, MongoDB } \\
      \textbf{Developer Tools / Platforms}{: VS Code, Git / Github, Amazon Web Services(AWS), Linux} \\
      \textbf{Technologies/Frameworks}{: React.js, Next.js, Express.js, Material-UI, React Bootstrap} \\
    }}
\end{itemize}
\vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Fraternity}{August 2020 -- January 2021}{Club Convener}{Avant (Programming Club)}
            \resumeItemListStart
                \resumeItem{Contributed algorithmic questions in the contests held on HackerRank indulging about 100+ participants each time.}
                \resumeItem{Organized a UI/UX Competition to promote the field of Front-end Development in the institute having 20+ registrations.}
            \resumeItemListEnd
        \resumeSubheading{Fraternity}{August 2020 -- Present}{Member}{Google Developer Student Clubs (DSC) IIIT Guwahati}
            \resumeItemListStart
                \resumeItem{Conducted a workshop on Web Development where I showed how to generate a Resume/CV (HTML File and PDF File) using basics of Node.js and helped the attendees in making a File Organizer based on their type extensions having 450+ views on YouTube on the first day as part of DSC Explore Event Chain.}
            \resumeItemListEnd
        \resumeSubheading{Volunteer}{August 2020}{Technical Writer}{The Curriculum Vitae (Newsletter)}
            \resumeItemListStart
                \resumeItem{Written technical articles on the topic "The New CORONA(Contact-less, Online, Remote, well Networked and Automated) Way Of Life" giving a overview on recent technology domain surges and "How Coronavirus Accelerated the New Industrial Revolution?" discussing how the pandemic can spur new advancements and can be found on iiitg-blogs.com.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
